---
title: "Developing Data Products Course Project: Shiny Application and Reproducible Pitch"
author: "Sreenivasulu Parimi"
date: "July 7, 2018"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Application Overview

This is BMTC (Bangalore Metropolitan Transport Corporation) route map presentation. This application helps to draw a route map of bmtc route numbers.

## How it works?

- This application written in Shiny which is a web application framework for R
- The source code contains two files: **ui.R** and **server.R**
- **ui.R** define UI for application that draws a bmtc route map
- **server.R** define server logic required to draw a bmtc route map
- This application leverages **BMTC Route Data** and **leaflet** for displaying the route map
- The application is hosted on Rstudio's Shiny server in the cloud (Shinyapps.io)

## Slide with Code/Output

```{r cars, echo = TRUE}
library(leaflet)
#library(dplyr)
bmtc_routes <- read.csv("bmtc_routes.csv", stringsAsFactors = FALSE)
bmtc_300A <- bmtc_routes[bmtc_routes$route_no == "300A",]
bmtc_300A_route_map <- leaflet() %>%
      addTiles()
bmtc_300A_route_map <- bmtc_300A_route_map %>%
      addMarkers(
            lat = as.numeric(bmtc_300A[3][[1]]),
            lng = as.numeric(bmtc_300A[4][[1]]),
            popup = as.character(bmtc_300A[2][[1]])
      )
bmtc_300A_route_map
```

## References

* Application URL: https://sreenivasulu-parimi.shinyapps.io/bmtcApp/
* Github Repository URL: https://github.com/sreenivasulu-parimi/Developing-Data-Products-Course-Project